\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-09-30 paper.qmd
Updated Figure 7 title

<!-- langevitour with pD model for two-curvy clusters -->
```{r}
#| label: best-fit-umap1
#| fig-cap: "Model in \\gD{} ($a_1 = 0.12$), on the layout and two views of the fit in projections from $7\\text{-}D$, for the two-curvy clusters data ($n =  2000$ and $p = 7$). One view shows the fitted model, and the other shows the fitted and true models alongside the data. The fitted model accurately represents the shape of the clusters but does not capture the edges of the structure. This illustrates a characteristic of UMAP, which compresses the data when transforming the data into \\gD{}."
#| fig-width: 10
#| fig-height: 10

@@

```{r}
#| echo: false
#| label: fig-predict-two-curvy
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| fig-cap: "Comparison of prediction generated using the exiting `umap` prediction method and our method: (a) A view of the true model in projections from $7\\text{-}D$, (b) predicted data from the `umap` prediction method, (c) predicted data from our method, and (d) comparison of predictions from both methods. In plot (d), points representing the same data but predicted by different methods are connected by lines. Need to add concluded sentence after changing the data."

>>>>

<!-- langevitour with pD model for two-curvy clusters -->
```{r}
#| label: best-fit-umap1
#| fig-cap: "Model in \\gD{} ($a_1 = 0.12$), on the layout and two views of the fit in projections from $7\\text{-}D$, for the two-curvy clusters data ($n =  2000$ and $p = 7$). One view shows the fitted model, and the other shows the fitted and true models alongside the data. The fitted model accurately represents the shape of the clusters but does not capture the edges of the structure. This illustrates a characteristic of UMAP, which compresses the data when transforming the data into \\gD{}. Video of the langevitour animations is available at <>."
#| fig-width: 10
#| fig-height: 10

@@

```{r}
#| echo: false
#| label: fig-predict-two-curvy
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| fig-cap: "Comparison of prediction generated using the exiting `umap` R package's prediction method and our method: (a) A view of the true model in projection from $7\\text{-}D$, (b) predicted data from the `umap` prediction method, (c) predicted data from our method, and (d) comparison of predictions from both methods. In plot (d), points representing the same data but predicted by different methods are connected by lines. Both prediction methods work similarly within the clusters, as each method predicts the data within the cluster with slight differences."

### 2024-09-30 paper.tex
Updated Figure 7 title

\caption{Model in \gD{} (\(a_1 = 0.12\)), on the layout and two views of
the fit in projections from \(7\text{-}D\), for the two-curvy clusters
data (\(n =  2000\) and \(p = 7\)). One view shows the fitted model, and
the other shows the fitted and true models alongside the data. The
fitted model accurately represents the shape of the clusters but does
not capture the edges of the structure. This illustrates a
characteristic of UMAP, which compresses the data when transforming the
data into \gD{}.}

@@

\caption{\label{fig-predict-two-curvy}Comparison of prediction generated
using the exiting \texttt{umap} prediction method and our method: (a) A
view of the true model in projections from \(7\text{-}D\), (b) predicted
data from the \texttt{umap} prediction method, (c) predicted data from
our method, and (d) comparison of predictions from both methods. In plot
(d), points representing the same data but predicted by different
methods are connected by lines. Need to add concluded sentence after
changing the data.}

>>>>

\caption{Model in \gD{} (\(a_1 = 0.12\)), on the layout and two views of
the fit in projections from \(7\text{-}D\), for the two-curvy clusters
data (\(n =  2000\) and \(p = 7\)). One view shows the fitted model, and
the other shows the fitted and true models alongside the data. The
fitted model accurately represents the shape of the clusters but does
not capture the edges of the structure. This illustrates a
characteristic of UMAP, which compresses the data when transforming the
data into \gD{}. Video of the langevitour animations is available at
\textless\textgreater.}

@@

\caption{\label{fig-predict-two-curvy}Comparison of prediction generated
using the exiting \texttt{umap} R package's prediction method and our
method: (a) A view of the true model in projection from \(7\text{-}D\),
(b) predicted data from the \texttt{umap} prediction method, (c)
predicted data from our method, and (d) comparison of predictions from
both methods. In plot (d), points representing the same data but
predicted by different methods are connected by lines. Both prediction
methods work similarly within the clusters, as each method predicts the
data within the cluster with slight differences.}
